HERMES : Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2022-01-03 hermes_paper/hermes_ieee.tex
Final corrections

\subsection{Translate fashion to data}
\label{sec:dataset:a}
A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc. Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere. To finely represent human behaviours based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations. Analyzing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where vision algorithms detected the fashion trend on picture.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.

@@

Due to the increasing use of social media and users' change of behaviour, a normalization step is applied to the raw sequences. Each fashion trend is divided by its hierarchical parent category trend. Moreover, in order to not remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization. For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China. The final normalized sequence is expressed in share of category.

We therefore introduce a new dataset for fashion time series forecasting.  It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, in 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. this collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. For instance, some sequences show complex behaviours with sudden changes (emerging or declining trends). A central point of this work is to accurately detect and forecast such trends.

@@

In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. In this way, a weak signal for each sequence is added to the proposed dataset.

Numerous social media influencers were selectioned by hand by fashion experts. By aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. We named \textit{fashion-forwards} this weak signal.  For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel. For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.

@@

\subsection{Training}
The dataset is temporally split into three blocks, {\em train}, {\em eval} and {\em test} sets. The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year. The hybrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
Using the two first years of the {\em train} set, a first per-time-series parametric model for each time series is fitted. With the resulting collection of local models, a forecast of the third year is computed for each sequence. Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts. For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and forecasts of the fourth year are computed. The {\em eval} set is used during the training to control the learning of the RNN model and prevent overfitting. The per-time-series predictors are fitted a last time for the {\em test} set using the four first years. The final accuracy measures of all our models are computed on this {\em test} set. As an illustration, an example of our temporal split is shown in Figure~\ref{fig:train_eval_test_set}.

For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.  Depending of the choice of local parametric models, two versions of HERMES are proposed. The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves the best accuracy results on the fashion dataset. The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension. A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follows:
$$
\ell(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
$$
This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors. The loss and previous parameters are all set with a grid search (additional materials can be found in Appendix). The code is developed in Python using the Tensorflow library. It allows the use of GPU to speed up the training process.

@@

To compare the different methods, we use the Mean Absolute Scaled Error (MASE). As our time series have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence. The MASE metric is defined as follows, with $m$ the seasonal periods:
\begin{align*}
\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
\end{align*}
Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not. In a given year, an increasing trend is defined as a trend that does more than 5\% of growth with respect to the previous year. In the same way, a decreasing trend is defined as a trend that declines by 5\% or more. Other trends are classified as flat trends. With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends. On the {\em test} set, for each method, the accuracy is defined as follows:
\begin{align*}
\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
\end{align*}
where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.

@@

Models using our weak signals perform similarly as without-weak-signals models for the MASE.  Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} model and some weaknesses that can be corrected.

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural network, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
%  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{ACCURACY}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:metricresults}
\end{table}

@@

First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets. Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting some of TBATS weaknesses and logically reaches a satisfactory final accuracy. Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases. On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level. Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amounts of data to do so. Nevertheless, with the HERMES framework, the RNN task is largely simplified. Our model logically needs less data to be trained and to obtain interesting performance.

@@

\textbf{Training. } The M4 dataset is firstly preprocessed in order to equalize all the sequences. This preliminary step is motivated by two reasons. First, as some sequences are short (93 time steps), they limit the window size $w$ of the RNN part and consequently the global accuracy of the HERMES approach. Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS. 300 time steps are kept for each sequence in order to train the HERMES model. For the shorter sequences, the train set is duplicated in order to reach the length of 300. For the longer ones, they are cropped in order to keep the last 300 time steps.
%The sequences are firstly resized in order to obatain a dataset with fixed time horizon. The eval and the test sets are removed for the shortest sequences (the last 26 steps). Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}. As per time series parametric model training time depends on the sequence length, all time series are then croped. Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.

The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is set to 104. For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used. The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8. As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results. 3 windows are computed for each sequence for the RNN train set. An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{sec:m4gridsearch}.

@@

\textbf{Benchmarks. } The M4 competition provides a rich collection of benchmarks emcompassing statistical models and neural network approaches. The same candidates are used in this part as baselines. In addition, the hybrid model named \textit{Uber} of S.Smyl is added. For a complete description and references of the benchmark models, see \cite{makridakis2020m4}. As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}. Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure. A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.

\textbf{Results and discussion. } The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarks. This result is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With this second application, two important conclusions can be made. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

@@

\section{Conclusion}
\label{sec:conclusion}
The motivation of this paper was to present HERMES, a new hybird model for time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification. In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential. By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with huge changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. An interesting perspective is to add a latent discrete label to select dynamically the regime shifts, i.e. which corrector model to use on-the-fly.

@@

The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes. An overview of the dataset is given in Table~\ref{tab:m4dataset} and some example of sequences are given in Figure~\ref{fig:m4examples}. As sequences have not the same domain origin, the HERMES approach doesn't seem to be the best suited model for this forecasting task. However, on some examples as in Figure~\ref{fig:m4pred}, interesting corrections of the Tbats forecasts can be noted.

@@

\begin{figure}
%\centering
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W10}
%  \caption{A time series from the ``Other`` category called \textit{W10}.}
  \label{fig:m4examples:sub1}
%\end{subfigure} \quad
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W20}
%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
%  \label{fig:m4examples:sub1}
%\end{subfigure}
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W220}
%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
%  \label{fig:m4examples:sub2}
%\end{subfigure}\quad
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W354}
%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
%  \label{fig:m4examples:sub3}
%\end{subfigure}
\caption{Examples of time series from the M4 weekly dataset. From Top to Bottom : time series called \textit{W10} from the \textit{Other} category,\textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category}
\label{fig:m4examples}
\end{figure}

@@

Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy. The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}. It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach to forecast it. With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset. A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}. A promising research perspective can be to replace the TBATS per-time-series predictor by this model which seems more suited for the M4 weekly forecasting task.

@@

In addition to the loss function, the HERMES model also depends on several hyperparameters to set correctly in order to reach satisfactory performance. For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{fig:m4parameter}. For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated. As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed. For the final \textit{hermes-tbats} model of the M4 weekly dataset, the grid searchs fixed the following set of parameters : 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.

>>>>

\subsection{Translate fashion to data}
\label{sec:dataset:a}
A collection of vision neural networks were designed and trained  at detecting clothes details on pictures: type of clothing (pants, shoes, tops, etc.), form, size, color, texture, etc. Then, fashion experts designed fashion trends by aggregating these clothes details: a meaningful combination of items that represent an existing trend in the fashion sphere. To finely represent human behaviours based on social media, a group of thousands of random users, called a panel, was created on several geolocalisations. Analyzing every day images shared on social networks by these panels with our computer vision algorithms, we can translate the history of thousands of fashion trends in thousands of time series.  All sequences have 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each value represents the number of users posts in a week where computer vision algorithms detected the fashion trend.  As an illustration, an example of fashion time series is given in Figure~\ref{fig:normalization}.

@@

Due to the increasing use of social media and behaviour changes, a normalization step is applied to the raw sequences. Each fashion trend is divided by its hierarchical parent category trend. Moreover, in order to not remove the seasonality of all sequences, we deseasonalized the hierarchical parent category trend before the normalization. For instance, as displayed in Figure~\ref{fig:normalization}, the raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China. The final normalized sequence is expressed in share of category.

We therefore introduce a new dataset for fashion time series forecasting.  It contains a sample of $\numberts$ anonymized and  normalized fashion trends for men and women, in 9 different categories and 5 geozones. An overview of it can be found in Table~\ref{tab:fashiondataset}. This collection of $\numberts$ fashion trends was selected in order to represent finely the issues faced by the fashion industry. For instance, some sequences show complex behaviours with sudden changes, referred to as emerging or declining trends. A central point of this work is to accurately detect and forecast such trends.

@@

In theoretical fashion dynamics \cite{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. %In this way, a weak signal for each sequence is added to the proposed dataset.
Numerous social media influencers were selectioned by hand by fashion experts. By aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. We named \textit{fashion-forwards} this weak signal.  For all trends $\{y_t\}_{1\leqslant t\leqslant T}$, let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for our hybrid model:  for all $n \in \{1,\ldots,N\}$, for all $t \in \{1,\ldots,T\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$
Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel. For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.

@@

\subsection{Training}
The dataset is split into three blocks, {\em train}, {\em eval} and {\em test} sets. The 3 first years are used as the {\em train} set, the 4th year is kept for the {\em eval} set and the {\em test} set is made of the last year. The hybrid model is trained to compute a one-year ahead prediction, $\lag$ equal to 52, and the window size $\window$ is fixed at 104.
Using the two first years of the {\em train} set, a first per-time-series parametric model for each time series is fitted. With the resulting collection of local models, a forecast of the third year is computed for each sequence. Corrector inputs are finally computed and the RNN is trained at correcting weaknesses of this first collection of third-year forecasts. For the {\em eval} set, per-time-series predictors are fitted a second time using the three first years and forecasts of the fourth year are computed. The {\em eval} set is used during the training to control the learning of the RNN model and prevent overfitting. The per-time-series predictors are fitted a last time for the {\em test} set using the four first years. The final accuracy measures of all our models are computed on this {\em test} set. As an illustration, an example of our split is shown in Figure~\ref{fig:train_eval_test_set}.

For the first parametric per-time-series models, existing Python or R libraries are used to estimate the different parameters $\statparam^n$.  Depending of the choice of local parametric models, two versions of HERMES are proposed. The first one uses as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one uses the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves the best accuracy results on the fashion dataset. The neural network architecture is summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layers of shape 50 and a final Dense layer to provide the correct output dimension. A classical Adam optimizer is used with a learning rate set at 0.001 or 0.005, the batch size is fixed 64 and the loss function is defined as follows:
$$
\ell(\ts^n_{T+1:T+\lag},\tspred^n_{T+1:T+\lag|T}) = \frac{1}{\meants^n_T}\sum_{i=1}^{\lag}|\ts^n_{T+i} - \tspred^n_{T+i|T}|\,.
$$
This choice of $\mathrm{L}_1$  loss function is motivated by its robustness to outliers which accounts for some time series in the fashion industry with very specific behaviors. The loss and previous parameters are all set with a grid search (additional materials can be found in the Appendix). The code is developed in Python using the Tensorflow library. It allows the use of GPU to speed up the training process.

@@

To compare the different methods, we use the Mean Absolute Scaled Error (MASE). As our time series have completely different scales, from $10^{-5}$ to $10^{-1}$, this metric was chosen to compute a fair error measure, independent of the scale of the sequence. The MASE metric is defined as follows, with $m$ the seasonal periods:
\begin{align*}
\mathrm{MASE} &= \frac{T-m}{h}\frac{\sum_{i=1}^h |Y_i - \hat{Y}_i| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,.
\end{align*}
Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In addition to the MASE accuracy metric, the different methods are also evaluated on a classification task and especially differences between methods using weak signals or not. In a given year, an increasing trend is defined as a trend that does more than 5\% of growth on average with respect to the previous year. In the same way, a decreasing trend is defined as a trend that declines by 5\% on average or more. Other trends are classified as flat trends. With this threshold, the proposed fashion dataset is almost balanced on the {\em test} set: There are 3087 increasing trends, 3342 decreasing trends and 3571 flat trends. On the {\em test} set, for each method, the accuracy is defined as follows:
\begin{align*}
\mathrm{ACCURACY} &= \frac{TP}{TP + FP}\,,
\end{align*}
where $TP = TP_{dec} + TP_{flat} + TP_{inc}$ and $FP = FP_{dec} + FP_{flat} + FP_{inc}$ with $TP_i$  the number of time series correctly classified in the class $i$ and $FP_i$ the number of time series misclassified in the class $i$.

@@

Models using our weak signals perform similarly as without-weak-signals models for the MASE.  Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
%  \resizebox{0.85\textwidth}{!}{%
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE}} &&& \multicolumn{3}{c}{\textbf{ACCURACY}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
%    \hline
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.805 && -&&& 0.449 && - & \\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
    %\hline
  \end{tabular}
%  }
\label{tab:metricresults}
\end{table}

@@

First, the hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets. Due to the strength of its per-time-series predictor TBATS, the hybrid model succeeds at correcting TBATS  and reaches a satisfactory final accuracy. Secondly, we can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases. On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms its accuracy level. Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require  large amounts of data to do so. Nevertheless, with the HERMES framework, the RNN task is largely simplified. Our model needs less data to be trained and to obtain interesting performance.

@@

\textbf{Training. } The M4 dataset is firstly preprocessed. This preliminary step is motivated by two reasons. First, as some sequences are short (93 time steps), they limit the window size $w$ of the RNN part and consequently the global accuracy of the HERMES approach. Second, the longer time series slow down the training of the collection of the first predictors especially for complex methods like TBATS. We kept 300 time steps  for each sequence in order to train the HERMES model. For the shorter sequences, the train set is duplicated in order to reach the length of 300. Longer sequences are cropped in order to keep the last 300 time steps.
%The sequences are firstly resized in order to obatain a dataset with fixed time horizon. The eval and the test sets are removed for the shortest sequences (the last 26 steps). Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}. As per time series parametric model training time depends on the sequence length, all time series are then croped. Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.

The horizon $h$ is set to 13  and the window size $w$ is set to 104. For the RNN part, the same architecture as the one described in Figure~\ref{fig:rnn_architecture} is used. The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8. As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results. Three windows are computed for each sequence for the RNN train set. An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{fig:m4dataset}.
The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{sec:m4gridsearch}.

@@

\textbf{Benchmarks. } The M4 competition provides a rich collection of benchmarks emcompassing statistical models and neural network approaches. The same candidates are used in this part as baselines. In addition, the hybrid model named \textit{Uber} of S.Smyl is added. For a complete description and references of the benchmark models, see \cite{makridakis2020m4}. As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}. Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures. A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{sec:m4overview} for additional information about the M4 weekly dataset.

\textbf{Results and discussion. } The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. The HERMES approach \textit{hermes-tbats} outperforms all the benchmarks. This result is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With this second application, two important conclusions can be made. Firstly, the results provided by \textit{hermes-tbats} confirm that the HERMES approach is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

@@

\section{Conclusion}
\label{sec:conclusion}
The motivation of this paper was to present HERMES, a new hybird model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification. In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential. By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with huge changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. An interesting perspective is to add a latent discrete label to select dynamically the regime shifts.

@@

The M4 weekly dataset is a collection of 359 time series with  contrasting behaviours and sizes. An overview of the dataset is given in Table~\ref{tab:m4dataset} and some examples of sequences are given in Figure~\ref{fig:m4examples}. As sequences come from a wide diversity of sectors, the forecasting task is very challenging. However, on some examples as in Figure~\ref{fig:m4pred}, efficient corrections of the TBATS forecasts can be obtained.

@@

\begin{figure}
%\centering
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W10}
%  \caption{A time series from the ``Other`` category called \textit{W10}.}
  \label{fig:m4examples:sub1}
%\end{subfigure} \quad
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W20}
%  \caption{A time series from the ``Macro`` category called \textit{W20}.}
%  \label{fig:m4examples:sub1}
%\end{subfigure}
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W220}
%  \caption{A time series from the \textit{Finance} category called \textit{W220}.}
%  \label{fig:m4examples:sub2}
%\end{subfigure}\quad
%\begin{subfigure}{.45\textwidth}
%  \centering
  \includegraphics[width=1.\linewidth]{figure/W354}
%  \caption{A time series from the \textit{Micro} category called \textit{W354}.}
%  \label{fig:m4examples:sub3}
%\end{subfigure}
\caption{Examples of time series from the M4 weekly dataset. From Top to Bottom : time series called \textit{W10} from the \textit{Other} category, \textit{W20} from the \textit{Macro} category, \textit{W220} from the \textit{Finance} category and \textit{W354} from the \textit{Micro} category.}
\label{fig:m4examples}
\end{figure}

@@

Looking at the final result of the M4 competition, some models reach a higher accuracy than the HERMES framework on the weekly dataset. Except one approach, all of them are a combination of different models in order to increase the robustness of the final forecast and at the same time achieve a better global accuracy. The remaining one is not an ensembling but a statistical framework called \textit{Forecast Pro}. It is not a single statistical model but a framework that chooses, depending on the sequence properties, the best statistical approach. With a OWA equal to 0.739, it outperforms the \textit{hermer-tbats} and all the M4 proposed models on the M4 weekly sub-dataset. A description and interesting remarks about the \textit{Forecast Pro} model are discussed in \cite{DARIN2020135}. This model offers an interesting research perspective specifically for the M4 weekly forecasting task.

@@

In addition to the loss function, the HERMES model also depends on several hyperparameters to set correctly in order to reach satisfactory performance. For instance, an overview of the learning rate, batch size and number of windows per time series grid search for the M4 weekly dataset is shown in Figure~\ref{fig:m4parameter}. For each parameter, a collection of 10 \textit{hermes-tbats} models have been trained with a range of values and the final OWA was calculated. As in the Figure~\ref{fig:loss_function}, the mean and the standard deviation of each group of 10 trainings is computed. For the final \textit{hermes-tbats} model of the M4 weekly dataset,  the following set of parameters was selected: 3 windows per time series were used as the train set, the batch size was set to 8 and the learning rate was fixed to 0.005.
